How Slow do my Transient Type Checks Go?

### 2019-08-17 paper.tex
intro of sec. 4
Signed-off-by: Stefan Marr <git@stefan-marr.de>

\section{Results}
\label{s-overall}

\begin{figure*}
	\input{graphs/full-scatter}
	\caption{Graphs of (at most) 102 configurations in the typing lattices for each benchmark. Time is measured as the mean of the 351\textsuperscript{st} to the 1,000\textsuperscript{th} benchmark iteration under a single invocation of Moth (lower is better).}
	\label{f:full}
\end{figure*}
The results for the performance of our sample of typing lattice configurations are presented in figure~\ref{f:full}. Following \cite{vitousek-transient-arXive-2019}, the points on each graph show the average execution of each individual configuration. The x-axis represents the proportion of type annotations for each configuration, with the left- and right-most points showing the times for the fully untyped and typed configurations respectively. The execution time in milliseconds is shown on the left y-axes, and time relative to the fully untyped configuration is shown on the right y-axes.

>>>>

\section{Performance of Benchmark Configurations}
\label{s-overall}

\begin{figure*}
	\input{graphs/full-scatter}
	\caption{Graphs of (at most) 102 configurations in the typing lattices for each benchmark. Time is measured as the mean of the 351\textsuperscript{st} to the 1,000\textsuperscript{th} benchmark iteration under a single invocation of Moth (lower is better).}
	\label{f:full}
\end{figure*}

Before we start to investigate specific type annotations,
we present the performance measurements of our sample of the typing lattice configurations in figure~\ref{f:full}.
These results are the foundation for a more details analysis.

Following \cite{vitousek-transient-arXive-2019}, the points on each graph in figure~\ref{f:full} show the average execution of each individual configuration. The x-axis represents the proportion of type annotations for each configuration, with the left- and right-most points showing the times for the fully untyped and typed configurations respectively. The execution time in milliseconds is shown on the left y-axes, and time relative to the fully untyped configuration is shown on the right y-axes.
